HyperLogLog: Exponentially Bad in Adversarial Settings

### 2020-10-21 docs/HLL_exp_bad/main.tex
making a non-anon version

\title{HyperLogLog: Exponentially Bad in Adversarial Settings}
%\author{Kenneth G. Paterson and Mathilde Raynal\\
%\vspace{3mm}
%Department of Computer Science, ETH Zurich\\
%{\tt kenny.paterson@inf.ethz.ch, mraynal@student.ethz.ch}}

@@

\begin{lemma}\label{lem:bound}
Suppose an adversary inserts elements $x$ from some set ${\cal X}$ into an initially empty HLL sketch. Suppose the adversary can guarantee that in its attack, only a subset of size $B$ out of $2^m$ buckets are hit, where $B \leq B_{\max}$ with 
\[
B_{\max} := \left\lfloor m\cdot\left(1-\frac{2\alpha_m}{5}\right)\cdot\left(1-2^{-(\ell+1)}\right)^{-1} \right\rfloor. \label{eqn:1} 
\]
Then, at the end of the attack, the HLL cardinality estimate is at most $m \cdot \ln (m/V)$ where $V = m-B$.
\end{lemma}

>>>>

\title{HyperLogLog: Exponentially Bad in Adversarial Settings}
\author{{\rm Kenneth G. Paterson}\\ {\rm ETH Zurich} \and {\rm Mathilde Raynal\thanks{Work done while an exchange student at ETH Zurich.}}\\ {\rm EPFL}}
%{\tt kenny.paterson@inf.ethz.ch, mraynal@student.ethz.ch}}

@@

\begin{lemma}\label{lem:bound}
Suppose an adversary inserts elements $x$ from some set ${\cal X}$ into an initially empty HLL sketch. Suppose the adversary can guarantee that in its attack, only a subset of size $B$ out of $m$ buckets are hit, where $B \leq B_{\max}$ with 
\[
B_{\max} := \left\lfloor m\cdot\left(1-\frac{2\alpha_m}{5}\right)\cdot\left(1-2^{-(\ell+1)}\right)^{-1} \right\rfloor. \label{eqn:1} 
\]
Then, at the end of the attack, the HLL cardinality estimate is at most $m \cdot \ln (m/V)$ where $V = m-B$.
\end{lemma}
